Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2014-12-04 paper.tex
Add png to paper
modify paper

\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

@@

@@

>>>>

\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
   \graphicspath{{./png/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

@@

\includegraphics[width=10cm]{net5}

@@

\section{Samples}
For showing obilious performance ratio with energy constraint really make a difference in the switching off link 
process, we will explain it in two simple topologies, cliques and cycles. On the other hand, we also say that
there will be an upper bound for obilious performance ratio with energy constraint, and get the bound according
to the topology.

Cycles topology connect all the nodes by a cycle, any node in which has two links joined. Figure 1 show the six
nodes cycles topology, let nodes named from $A$ to $F$ and links named by its two vertices, such as $l_{ab}$.
Without loss of generality,
